Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-04-28 paper/referee_report_1/response.md

Dear editor,

We thank the referee for the many detailed comments, which we have tried to address in this revised version. In many instances, the referee asked for a more thorough analysis, particularly surrounding the nulling phenomenon, which -- now that the paper is being submitted to the main journal (instead of Letters) there has been room to include, and we believe the paper is much better for it. In a few cases, however, we have deferred the suggested deeper analysis until the planned follow-up paper, which will benefit from an expanded data set and a wider frequency coverage. Please fine our detailed response to the referee's comments below.

Sincerely,
~/Sam

-------------------------------------------------------

### 2022-04-28 paper/main.tex
Added a thankyou to the referee in the acknowledgements
Fixed typo in paper

{\bf
Pulsars that both show complicated drifting behavior and which are bright enough for single pulse analysis, are relatively rare.
}
Even a cursory glance at the drift bands of \psr{} show that its drifting behavior is indeed complex and bright, making it a welcome addition to this category of pulsar.
{\bf 
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to sub-pulse drifting, originally noticed by \citep{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, J1822$-$2256 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.
}

@@

\begin{acknowledgements}
% MWA
This scientific work makes use of the Murchison Radio-astronomy Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site. Support for the operation of the MWA is provided by the Australian Government (NCRIS), under a contract to Curtin University administered by Astronomy Australia Limited.
% Pawsey
We acknowledge the Pawsey Supercomputing Centre which is supported by the Western Australian and Australian Governments.
% OzSTAR
This work was supported by resources awarded under Astronomy Australia Ltd's ASTAC merit allocation scheme on the OzSTAR national facility at the Swinburne University of Technology. The OzSTAR program receives funding in part from the Astronomy National Collaborative Research Infrastructure Strategy (NCRIS) allocation provided by the Australian Government.
% GMRT
The GMRT is run by the National Centre for Radio Astrophysics
of the Tata Institute of Fundamental Research, India.
% ADACS
Software support resources awarded under the Astronomy Data and Computing Services (ADACS) Merit Allocation Program.
ADACS is funded from the Astronomy National Collaborative Research Infrastructure Strategy (NCRIS) allocation provided by the Australian Government and managed by Astronomy Australia Limited (AAL).
% DK + Alex McEwen
DK was supported by NSF grant AST-1816492.
We would also like to thank Alex McEwen for making the original discovery of this pulsar in the GBNCC survey.
%RMS
RMS acknowledges support through Australian Research Council Future Fellowship FT190100155.
\end{acknowledgements}

>>>>

{\bf
Pulsars that both show complicated drifting behavior and are bright enough for single pulse analysis, are relatively rare.
}
Even a cursory glance at the drift bands of \psr{} show that its drifting behavior is indeed complex and bright, making it a welcome addition to this category of pulsar.
{\bf 
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to sub-pulse drifting, originally noticed by \citep{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, J1822$-$2256 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.
}

@@

\begin{acknowledgements}
% MWA
This scientific work makes use of the Murchison Radio-astronomy Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site. Support for the operation of the MWA is provided by the Australian Government (NCRIS), under a contract to Curtin University administered by Astronomy Australia Limited.
% Pawsey
We acknowledge the Pawsey Supercomputing Centre which is supported by the Western Australian and Australian Governments.
% OzSTAR
This work was supported by resources awarded under Astronomy Australia Ltd's ASTAC merit allocation scheme on the OzSTAR national facility at the Swinburne University of Technology. The OzSTAR program receives funding in part from the Astronomy National Collaborative Research Infrastructure Strategy (NCRIS) allocation provided by the Australian Government.
% GMRT
The GMRT is run by the National Centre for Radio Astrophysics
of the Tata Institute of Fundamental Research, India.
% ADACS
Software support resources awarded under the Astronomy Data and Computing Services (ADACS) Merit Allocation Program.
ADACS is funded from the Astronomy National Collaborative Research Infrastructure Strategy (NCRIS) allocation provided by the Australian Government and managed by Astronomy Australia Limited (AAL).
% DK + Alex McEwen
DK was supported by NSF grant AST-1816492.
We would also like to thank Alex McEwen for making the original discovery of this pulsar in the GBNCC survey.
%RMS
RMS acknowledges support through Australian Research Council Future Fellowship FT190100155.
We thank the anonymous referee for the many detailed suggestions which improved this paper.
\end{acknowledgements}
